---
title: "Food & CO2"
author: "Renaud Liber"
date: "22-2-2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r libraries}
library(tidyverse)
library(plotly)
library(countrycode)
library(janitor)


```


```{r}
raw_food_consumption <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-18/food_consumption.csv')

food_consumption <- raw_food_consumption %>% 
  mutate(food_category=as_factor(food_category),
         country=as_factor(country),
         co2_by_kg=round(co2_emmission/consumption,1))
```



variable	class	description

country	character	Country Name
food_category	character	Food Category
consumption	double	Consumption (kg/person/year)
co2_emmission	double	Co2 Emission (Kg CO2/person/year)


Finland, Lithuania and Sweden as the three top consumers in term of weight food but when looking at Lithuania, we can see that they are producing half of the CO2.


```{r}

summary_country <- food_consumption %>% 
  group_by(country) %>% 
  summarise(Tot_consumption=sum(consumption),
            Tot_co2_emmission=sum(co2_emmission)) %>% 
  arrange(-Tot_consumption)


food_consumption %>% 
  filter(country=="Finland")

food_consumption %>% 
  filter(country=="Lithuania")

food_consumption %>% 
  filter(country=="Sweden")


```



Lithuania consume almost no beef compared to the other three top countries.
This what drives really the difference

Other interesting element is the high consumption of Milk including cheese in Finland this drives their C02 emission

Other point is that it seems that emission are greater for Goat & Lamb. But when looking at other sources http://www.fao.org/3/i3461e/i3461e04.pdf  page 37) - it seems that it might be overstated

Lastly, as we will see later - though those countries are consuming a high "weight" of food - they are not in the anyways in the top C02 emission


```{r}

g_top_consumer <- summary_country %>% 
  top_n(3, Tot_consumption) %>% 
  ungroup() %>%
  select(country) %>% 
  left_join(food_consumption,by="country") %>% 
  pivot_longer(cols = consumption:co2_by_kg,
               names_to = "KPI") %>% 
  filter(!is.na(value)) %>% 
  mutate(beef=if_else(food_category=="Beef",TRUE,FALSE)) %>% 
  filter(!is.na(value)) %>% 
  mutate(food_category=fct_reorder(food_category,value)) %>% 
  ggplot(aes(food_category,value,fill=beef))+
  geom_col()+
  facet_grid(country~KPI, scales="free"
             )+
  coord_flip()+
  scale_fill_manual(values = c("darkgrey","red"))+
  theme(legend.position = "none")

 ggplotly(g_top_consumer) 

```


What are the countries that consume the most beef and the lamb as those produced most C02

Argentina, Brazil & US are the most beef consumer - but did not appear in my top countries - how come?


```{r}

food_consumption %>% 
  filter(food_category=="Lamb & Goat") %>% 
  arrange(-consumption)


food_consumption %>% 
  filter(food_category=="Beef") %>% 
  arrange(-consumption)

```


We can see here that the beef is the element that 

```{r}

select_countries <- c("Brazil", "Argentina", "USA","Finland")
 
  
  
g_top_emission <- summary_country %>% 
top_n(3, Tot_co2_emmission) %>% 
  ungroup() %>%
  select(country) %>% 
  left_join(food_consumption,by="country") %>% 
  pivot_longer(cols = consumption:co2_by_kg,
               names_to = "KPI") %>% 
  mutate(beef=if_else(food_category=="Beef",TRUE,FALSE)) %>% 
  filter(!is.na(value)) %>% 
  mutate(food_category=fct_reorder(food_category,value)) %>% 
  ggplot(aes(food_category,value,fill=beef))+
  geom_col()+
  facet_grid(country~KPI, scales="free"
             )+
  coord_flip()+
  scale_fill_manual(values = c("darkgrey","red"))+
  theme(legend.position = "none")

 ggplotly(g_top_emission) 
 
```


```{r}


subplot(ggplotly(g_top_consumer),
        ggplotly(g_top_emission))
```



Create a model to define the continent of the country based on cunsumption

```{r}

food_consumption %>% 
  select(1:3) %>% 
  mutate(continent=countrycode(country,
                               origin = "country.name",
                               destination = "continent")) %>% 
  pivot_wider(names_from = food_category,values_from = consumption) %>% 
  clean_names() %>% 
  

```

