---
title: "2020-02-14-Hotel_Bookings"
author: "Renaud Liber"
date: "14-2-2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load libraries}
library(tidyverse)
library(skimr)
library(tsible)
library(plotly)
library(tidymodels)
library(correlationfunnel)
install.packages("tsibble")

install.packages("recipes")


theme_set(theme_light())
```



```{r import data}

hotels_raw <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-11/hotels.csv') 
```


```{r}
hotels <- hotels_raw %>% 
  inner_join(maps::iso3166 %>% select(a3,ISOname),
             by=c("country"="a3")) %>% 
  mutate(ISOname=as_factor(ISOname))


maps::iso3166 %>% 
  filter(sovereignty %>% str_detect("Port"))

```


```{r EDA}

hotels %>% skim()

hotels %>% glimpse()

```

Number of visit linked to repeated guest represent only 3% of the total visit

+ depending on number of customer (if only a handful, it might be worthwhile to do some limited marketing campaign - but would not be a focus point)

# 97% of the customers will come only once

```{r}
hotels %>% 
  count(is_repeated_guest) %>% 
  mutate(ratio=n/sum(n))

```


The dataset must be representing chains that are located in Portugal - 
62% of the tourists are from the country

```{r}
p <- hotels %>% 
  count(Visitor_Cntry=fct_lump(ISOname,10),sort = TRUE) %>% #Great trick to fct_lump quickly
  mutate(Visitor_Cntry=fct_reorder(Visitor_Cntry,n),
         label_text=str_glue("<b> Number of visitor : {n}</b>
                       Share of the total visit : {scales::percent(n/sum(n))}"),
         flag=if_else(Visitor_Cntry=="Portugal",TRUE,FALSE)) %>% 
  ggplot(aes(Visitor_Cntry,n,fill=flag))+
  geom_col()+
  coord_flip()+
  geom_col(aes(text=label_text)) +
  labs(title = "Most of the visit are in country")

p %>% 
  ggplotly(tooltip ="text")

  
```


#What correlate most to cancellation


```{r}

hotels %>% 
  DataExplorer::plot_missing()

```



# can we predict likelyhood of cancelation

We can see here the feature that correlate most to hotel cancellation. 
Reservation status should be excluded from the Analysis



```{r}

hotels %>% 
  select(-reservation_status_date) %>% 
  filter(!is.na(children)) %>% 
  binarize() %>% 
  correlate(is_canceled__1) %>% 
  correlationfunnel::plot_correlation_funnel()

  


```

