---
title: "NFL Stadium Attendance"
author: "Renaud Liber"
date: "4-2-2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(tidyverse)
library(DataExplorer)
library(ggridges)
```

```{r import data}
attendance_raw <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-04/attendance.csv')
standings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-04/standings.csv')
games <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-04/games.csv')

```

```{r}
attendance <- attendance_raw %>% 
mutate(team_name=as.factor(team_name))
```


# Data Quality Check

Overall Data is pretty good at first glance with exception of attendance tbl which as some missing element (Weekly attendance - could it be that it was without public?)
Tie as well is missing from Games detail but normal


```{r Data Quality check}

#Attendance
attendance %>% glimpse()
attendance %>% 
  DataExplorer::plot_missing()


standings %>% glimpse()
standings %>% 
  DataExplorer::plot_missing()


games %>% glimpse()
games %>% 
  DataExplorer::plot_missing()

```


# How attendance as varied through time

It seems that attendance was exponential from 2000 to 2007 but then dropped till 2010 to pick up again but dropped again in 2015.

What explain the drops or peak in 2007 and 2016?
What brought back a spike in 2010?

```{r}

attendance %>% 
  group_by(year) %>% 
  summarise(attendance=sum(weekly_attendance,na.rm = TRUE)) %>% 
  ungroup() %>% 
  ggplot(aes(year,attendance))+
  geom_line()+
  scale_y_continuous(labels=function(x) format(x, big.mark = ".", scientific = FALSE))

```

```{r}

attendance %>% 
  group_by(team_name,year) %>% 
  summarise(attendance=sum(weekly_attendance,na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(team_name=fct_reorder(team_name,attendance)) %>% 
  ggplot(aes(team_name,attendance))+
  geom_boxplot()+
  coord_flip()
  
```

