---
title: "Spotify_songs"
author: "Renaud Liber"
date: "28-3-2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(tidyquant)

library(tidymodels)


library(tidygraph)
library(ggraph)
library(networkD3)
library(DataExplorer)

```

```{r}
spotify_songs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-01-21/spotify_songs.csv')
```


```{r}
spotify_songs %>% 
  head()

spotify_songs %>% 
  glimpse()

```



```{r}
spotify_songs %>% 
  ggplot(aes(track_popularity)) +
  geom_bar()
```

We will filter the song that are equal to 0 as my end analysis will focus on songs that I would most likely like

```{r}
scored_songs <- spotify_songs %>% 
  filter(track_popularity!=0)
```

# Let's do some EDA

Who are the singer most popular

```{r}
scored_songs %>% 
  group_by(track_artist) %>% 
  summarise(avg_popularity=mean(track_popularity),
            n_songs=n()) %>% 
  arrange(-avg_popularity) %>% 
  filter(n_songs>20)
```
What are the key styles of the artist

```{r}

artist_genre <- scored_songs %>% 
  group_by(track_artist,playlist_genre) %>% 
  summarise(count_genre=n()) %>% 
  filter(count_genre>10)

#Try new excel function- no luck

# artist_genre %>% 
#   pivot_table(.rows = track_artist,
#               .columns = playlist_genre,
#               .values = count_genre) %>% 
#   kableExtra::kable()


artist_style_tbl <- artist_genre %>% 
  pivot_wider(names_from = playlist_genre,
              values_from = count_genre,
              values_fill = list(count_genre = 0))



```

Work on a matrix that will be used to segment/cluster group of artists

```{r}


mean_artist_genre <- artist_genre %>% 
  left_join(scored_songs,
            by = c("track_artist", "playlist_genre")) %>% 
  group_by(track_artist,playlist_genre) %>% 
  summarise(popularity_mean=mean(track_popularity),
            popularity_median=median(track_popularity),
            danceability=mean(danceability),
            energy=mean(energy),
            loudness=mean(loudness),
            speechiness=mean(speechiness),
            acousticness=mean(acousticness),
            instrumentalness=log(mean(instrumentalness)),
            liveness=mean(liveness)) %>% 
  arrange(-popularity_median) %>% 
  unite(col="Artist_genre",track_artist,playlist_genre,remove=FALSE)

```





# EDA 

```{r}

mean_artist_genre %>% 
  plot_histogram()


mean_artist_genre %>% 
  plot_missing()

```


Group song characteristics and center and scale
Speechiness, instrumentalness, liveness should all be log transformed

```{r}


# artist_matrix <- artist_style_tbl %>% 
#   right_join(mean_artist_genre,
#              by = "track_artist") 

# Individual transformations for skewness and other issues
# Discretize (if needed and if you have no other choice)
# Create dummy variables
# Create interactions
# Normalization steps (center, scale, range, etc)
# Multivariate transformation (e.g. PCA, spatial sign, etc)

rec_obj <- recipe(~.,data = mean_artist_genre) %>% 
  
  
  #adress log scales
  step_log(liveness,speechiness,acousticness) %>% 
  
  # Center and scale
  step_center(all_numeric()) %>% 
  step_scale(all_numeric()) %>% 
  step_dummy(playlist_genre) %>% 
  prep()


train_tbl <- bake(object = rec_obj,new_data = mean_artist_genre)

```

# Adjancncy Matrix

Prepare the Adjency matrix

```{r}

# Transpose Data to obtain artist similarity

artist_correlation_matrix <- train_tbl %>% 
  select(-track_artist,-instrumentalness) %>% 
  gather(key="Feature",value="value",-Artist_genre) %>% 
  spread(Artist_genre,value=value) %>% 
  select(-Feature) %>% 
  as.matrix() %>% 
  cor()


artist_correlation_matrix %>% as_tibble(rownames="Artist_genre")

```

Remove Customer that are equal to themselves

```{r}
diag(artist_correlation_matrix) <- 0
```

Remove duplicate items (lower part of correlation_matrix)
```{r}
artist_correlation_matrix[upper.tri(artist_correlation_matrix)] <- 0
```

Prune Relationship


```{r}
edge_limit <- 0.7

artist_correlation_matrix[artist_correlation_matrix<edge_limit] <- 0
artist_correlation_matrix %>% as_tibble(rownames="Artist")

```


```{r}
artist_relationship_tbl <- artist_correlation_matrix %>% 
  as_tibble(rownames = "from") %>% 
  gather(key="to",value="weight",-from) %>% 
  filter(weight>0)
```


# Recreate Worklfow as a function

```{r}
prep_corr_matrix <- function(correlation_matrix,edge_limit=0.8) {
  
  #Move Diag to 0
  diag(correlation_matrix) <- 0
  #Move Upper triangle to 0
  correlation_matrix[upper.tri(correlation_matrix)] <- 0
  #Move to 0 anything below edge limit 
  correlation_matrix[correlation_matrix<edge_limit] <- 0
  
  #Transpose matrix to table move from wide to long
  correlation_matrix %>% 
  as_tibble(rownames = "from") %>% 
  gather(key="to",value="weight",-from) %>% 
  filter(weight>0)
  
}


```


```{r}
prep_corr_matrix(artist_correlation_matrix,edge_limit = 0.85) %>% 
select(-weight) %>% 
  simpleNetwork()
```




```{r}
artist_correlation_matrix %>%
  
  prep_corr_matrix(edge_limit = 0.87) %>%
  
  as_tbl_graph(directed = FALSE) %>%
  
  ggraph(layout = "kk") +
  geom_edge_link(alpha = 0.5, color = palette_light()["blue"]) +
  geom_node_point(alpha = 0.5, color = palette_light()["blue"]) +
  theme_graph(background = "white") 
  

```


# Table Graph Manipulation

```{r}

artist_graph_tbl<- artist_correlation_matrix %>% 
   prep_corr_matrix(edge_limit = 0.87) %>%
    as_tbl_graph(directed = FALSE)

```

 Rank the node - not sure how key is that?

```{r}
artist_graph_tbl %>% 
  activate(nodes) %>% 
  mutate(node_rank=node_rank_traveller()) %>% 
  arrange(node_rank)


```

# 8.3 Grouping Nodes (Clustering)


```{r}



grouped_tbl_graph <- artist_graph_tbl %>%
    activate(nodes) %>%
    mutate(neighbors = centrality_degree()) %>%
    
    mutate(group = group_components()) %>%
    
    arrange(desc(neighbors)) %>%
    mutate(group_lump = group %>% as_factor() %>% fct_lump(n = 5))


grouped_tbl_graph %>%
    ggraph(layout = "kk") +
    geom_edge_link(alpha = 0.5) +
    geom_node_point(aes(color = group_lump), alpha = 0.5, size = 3) +
    
    theme_graph() +
    scale_color_tq(theme = "light") +
    theme(legend.position = "bottom") +
    labs(title = "Artist Network Detection")
```


# 9.0 COMMUNITY ANALYSIS ----
# - Join Communities and Inspect Key Features


```{r}


credit_card_group_tbl <- credit_card_tbl %>%
    left_join(as_tibble(grouped_tbl_graph), by = c("CUST_ID" = "name")) %>%
    select(group_lump, CUST_ID, everything()) %>%
    filter(!is.na(group_lump))

credit_card_group_tbl %>% glimpse()


plot_density_by <- function(data, col, group_focus = 1, ncol = 1) {
    
    col_expr <- enquo(col)
    
    data %>%
        mutate(focus = as.character(group_lump)) %>%
        select(focus, everything()) %>%
        mutate(focus = ifelse(as.character(focus) == as.character(group_focus), 
                                    "1", "Other")) %>%
        mutate(focus = as.factor(focus)) %>%
        
        ggplot(aes(!! col_expr, fill = focus)) +
        geom_density(alpha = 0.4) +
        facet_wrap(~ focus, ncol = ncol) +
        scale_fill_tq() +
        theme_tq()
}
```


