---
title: "UFO_Sightings"
author: "R.liber"
date: "7/1/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# install.packages("DataExplorer")
# install.packages("plotly")
# install.packages("geojsonio")
# installed.packages("rgeos")
# install.packages("mapproj")
# install.packages("openintro")
install.packages("prophet")

library(tidyverse)
library(DataExplorer)
library(plotly)
library(geojsonio)
library(rgeos)
library(rgeos)
library(broom)
library(mapproj)
library(openintro)
library(tidyquant)
theme_set(theme_tq())
```



```{r Import Data}

ufo_sightings <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-25/ufo_sightings.csv")

ufo_wrangled<- ufo_sightings %>% 
  
  mutate(date_time_2=mdy_hm(date_time) %>% date(),
          month_yy=floor_date(date_time_2,"year"),
         decade=round(lubridate::year(date_time_2)/10,0)*10,
         decade=decade %>% as.factor()
           )

ufo_wrangled %>% 
  glimpse

```


```{r}
ufo_sightings %>% 
  create_report()
```



#UFO sighthings through times

```{r}
 sighting_ts <- ufo_wrangled%>% 
  group_by(month_yy) %>% 
  summarise(n_sightings=n()) %>% 
  ggplot(aes(month_yy,n_sightings)) +
  geom_line(color="#18BC9C")+
  labs(title = "UFO sightings through time")

  
ggplotly(sighting_ts)    

```

It seems that UFO sightings only really wend exponantial from year 1980/1990
Diving into it further sightings really picked up in 1994 - year of the release of the "Roswell" TV serie

Data does not seem to be available from 2014 onward


```{r}

 ufo_wrangled%>% 
  group_by(decade) %>% 
  summarise(n_sightings=n()) %>% 
  ggplot(aes(decade,n_sightings)) +
  geom_col(fill="#18BC9C")

```

As previously spotted, sightings of UFO really started/were only reported from year 2000s


```{r Country were sightings happened}


 ufo_wrangled%>% 
  group_by(country) %>% 
  summarise(n_sightings=n()) %>% 
  mutate(country=country %>% replace_na("Not_Avail") %>% fct_reorder(n_sightings)) %>% 
  ggplot(aes(country,n_sightings)) +
  geom_col(fill="#18BC9C")+
  coord_flip()


```


Only 5 countries are provided within this data set, for the next analysis we will focus on us only.


```{r}
hexbin_us <- ufo_wrangled %>% 
  filter(country=="us",decade%in%c(2000,2010)) %>% 
  group_by(state) %>% 
  summarise(n_sightings=n()) %>% 
  mutate(state=state %>% abbr2state())

  spdf <- geojson_read("us_states_hexgrid.geojson",  what = "sp")
  spdf@data = spdf@data %>% mutate(google_name = gsub(" \\(United States\\)", "", google_name))
  
spdf_fortified <- tidy(spdf, region = "google_name") %>% 
  right_join(hexbin_us,by=c("id"="state"))
  
centers <- cbind.data.frame(data.frame(gCentroid(spdf, byid=TRUE), id=spdf@data$iso3166_2))


 
# Now I can plot this shape easily as described before:
ggplot() +
  geom_polygon(data = spdf_fortified, aes(fill=n_sightings, x = long, y = lat, group = group), color="white") +
  geom_text(data=centers, aes(x=x, y=y, label=id)) +
  theme_void() +
  coord_map()+
  scale_fill_gradient(low = "lightgreen", high = "#18BC9C") 
```

